Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment

### 2020-08-21 Cost_manuscript.Rmd
fixed and streamlined the optimization function for the adaptive model
discussion notes on fatigue

- What we think: subjective timing is shortened by the way we implemented cognitive effort. This can be recalibrated if many task types are experienced. Maybe the implementation allowed for counting. Alternatively, working memory engagement could produce timing issues (Buhi n Gershman). Also look at what Andrew Westbrook shared.
- Things that don't seem to be at play here, but could still play a general role in mental effort preferences: 1) A demand’s cost is not fully intrinsic (within vs between differences); 2) Effort preferences unlikely just due to learned industriousness or efficacy as amitais lab sees it (differences between effort types, and everyone met a good performance level per training); 3) avoiding boredom (global decline in exp 2, not a preference exchange). 4) Literally counting tasks, since mental effort was discretely presented but everything else was contiguous. If that were the case, dividing the handling time by 2 would work, but not sure if it would translated into exp 2.
- Deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effor aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains). Like, the aversion is due to focusing on different elements of the task.
- Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort
- It's true that we didnt calibrate cog effort per subject. But instead we brought all subjects to the same level of performance, and we saw that as time progressed they became less likely to accept longer periods of effort.

>>>>

- What we think: subjective timing is shortened by the way we implemented cognitive effort. This can be recalibrated if many task types are experienced. Maybe the implementation allowed for counting. Alternatively, working memory engagement could produce timing issues (Buhi n Gershman). Also look at what Andrew Westbrook shared. Add this to a potential fatigue, although that would also mean that waiting would be accepted less over time in exp 1.
- Things that don't seem to be at play here, but could still play a general role in mental effort preferences: 1) A demand’s cost is not fully intrinsic (within vs between differences); 2) Effort preferences unlikely just due to learned industriousness or efficacy as amitais lab sees it (differences between effort types, and everyone met a good performance level per training); 3) avoiding boredom (global decline in exp 2, not a preference exchange). 4) Literally counting tasks, since mental effort was discretely presented but everything else was contiguous. If that were the case, dividing the handling time by 2 would work, but not sure if it would translated into exp 2. 5) fatigue: there's a similar gradual decrease in acceptances in both experiments, except for the wait condition in exp 1. Fatigue would apply equally to both, or alternatively it might not bring all down to the same level (I guess the point could be made, but it's not that people who complete more at the beginning decrease acceptances more, as one would expect from fatigued people)
- Deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effor aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains). Like, the aversion is due to focusing on different elements of the task.
- Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort
- It's true that we didnt calibrate cog effort per subject. But instead we brought all subjects to the same level of performance, and we saw that as time progressed they became less likely to accept longer periods of effort.
